TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-02 CORL/example.tex
Added keywords
Fixed typo in comment
Added method section and +\acknowledgments{}
Unindented introduction
Moved citations to bottom
Added figures: frame_inconsistency_diagram.pdf and main_diagram.pdf

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\graphicspath{ {../images} }

@@

	% Because of the 6 senence limit, I've commented out some of the sentences...

	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
%
	%TURNING TWO SENTENCES INTO ONE:
	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
%
	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}

% Two or three meaningful keywords should be added here
\keywords{CoRL, Robots, Learning}

@@

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=270pt]{uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		 A UVL scene is an image that has three channels: RGB.
		 R and G are used for U and V, and B is used for L.
		 L stands for Label, and determines which part of the synthetic image will get which texture.
		 The U and V coordinates correspond to positions on each texture,
		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.

>>>>

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\graphicspath{ {../images} }

@@

	% Because of the 6 sentence limit, I've commented out some of the sentences...

	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
%
	%TURNING TWO SENTENCES INTO ONE:
	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
%
	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.

\end{abstract}

% Two or three meaningful keywords should be added here
\keywords{sim to real, image translation, differentiable rendering}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{frame_inconsistency_diagram.pdf}
	\end{center}
	\caption{
		Each row of images is a different random placement of object in a scene.
		Each column is a different image translation algorithm.
		The same cube is marked with the same color outline across all photos.
		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
		CUT and CycleGan are not consistent, while TRITON is.
		TODO: Update the images in this to have the latest training iteration...
		}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{uvl_explanation.pdf}
	\end{center}
	\caption{
		This diagram shows the purpose of a UVL image.
		 A UVL scene is an image that has three channels: RGB.
		 R and G are used for U and V, and B is used for L.
		 L stands for Label, and determines which part of the synthetic image will get which texture.
		 The U and V coordinates correspond to positions on each texture,
		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

\section{Method}
\label{sec:text}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{main_diagram.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper.
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4 
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
		}
	\label{fig:main_diagram}
\end{figure}

@@

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.
\acknowledgments{}
